The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-03-19 RET_Hosts_IR.tex

There are a limited number of events detected in the local Universe whose properties are consistent with the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Perley2019}. The transient declined from its discovery, with constraints on a ~1 day rise time, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova \replylluis{(KN; \citealt{Ho2019})}. There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova \replylluis{(CEJSN; \citealt{Soker2019})}; \replychris{or a wind-driven transient \citep{Ono2020}}.
Other nearby rapid transients include the local fast-declining SN-like transient \citep{McBrien2019} which is explained by the destruction of a white dwarf, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.  It is currently unclear whether these transients do indeed represent the local analogues of the DES and PS RETs.

@@

\subsection{Spectroscopy \label{subsec:spec}}
Accurate redshifts for DES-SN were obtained by OzDES, a dedicated DES spectroscopic follow-up campaign based at the $3.9~\textrm{m}$ Anglo-Australian Telescope (AAT) using the AAOmega fibre-fed spectrograph and 2dF fibre positioner. The observation strategy of OzDES was to point at one of the ten DES-SN fields, and place fibres at the positions of transient hosts, continually coadding the spectra of a particular host until a redshift was obtained at which point the fibre could be allocated to a different transient. The spectra have a resolution of 1400-1700 and a wavelength range of $3700~8800$~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts. \replychris{We use internal data release 7, a preliminary version of the public data release is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}. \replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA\footnote{\url{http://www.laduma.uct.ac.za}}) survey  \citep{Baker2020}, three of which are present in our sample} .
Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the GRC nontheless.  Where the spectra from which those redshifts were derived are also public they are included in this analysis. These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}) and SDSS. In total we analyse 42 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56/pixel. We stress that the emission lines are detected with a higher SNR than this.

>>>>

There are a limited number of events detected in the local Universe whose properties are consistent with the RETs seen in the samples of PS1 and DES at cosmological distances, the most widely studied of which is AT2018cow \citep[e.g.][]{Prentice2018,Perley2019}. The transient declined from its discovery, with constraints on a ~1 day rise time, and across the full range of observed wavelengths did not resemble any known SN, GRB afterglow, or kilonova \replylluis{(KN; \citealt{Ho2019})}. There are myriad explanations for the power source of AT2018cow touted in the literature, including: magnetars \citep{Mohan2020}; electron capture collapse of merged white dwarfs \citep{Lyutikov2019}; a tidal disruption event (TDE) of a white dwarf \citep{Kuin2019} or of a main sequence star by an intermediate mass black hole \citep{Perley2019}; common envelope jets supernova \replylluis{(CEJSN; \citealt{Soker2019})}; \replychris{or a wind-driven transient \citep{Uno2020}}.
Other nearby rapid transients include the local fast-declining SN-like transient \citep{McBrien2019} which is explained by the destruction of a white dwarf, and KSN-2015K \citep{Rest2018} whose fast rise and decline is explained by the shock of an SN running into previously-expelled material.  It is currently unclear whether these transients do indeed represent the local analogues of the DES and PS RETs.

@@

\subsection{Spectroscopy \label{subsec:spec}}
Accurate redshifts for DES-SN were obtained by OzDES, a dedicated DES spectroscopic follow-up campaign based at the $3.9~\textrm{m}$ Anglo-Australian Telescope (AAT) using the AAOmega fibre-fed spectrograph and 2dF fibre positioner. The observation strategy of OzDES was to point at one of the ten DES-SN fields, and place fibres at the positions of transient hosts, continually coadding the spectra of a particular host until a redshift was obtained at which point the fibre could be allocated to a different transient. The spectra have a resolution of 1400-1700 and a wavelength range of $3700~8800$~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts. \replychris{We use internal data release 7, a preliminary version of the public data release is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}. \replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA) survey\footnote{\url{http://www.laduma.uct.ac.za}}, three of which are present in our sample} .
Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the GRC nontheless.  Where the spectra from which those redshifts were derived are also public they are included in this analysis. These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}) and SDSS. In total we analyse 42 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56/pixel. We stress that the emission lines are detected with a higher SNR than this.
